## Do shorter titles lead to more citations?
> **Reviews:** Reading data, data frames, basic statistics in R, functions
>
> **Difficulty:** Medium

Adrian Letchford and colleagues (Roy Soc Open Science, 2015) found an interesting pattern: papers that have shorter titles tend to fare better in terms of citations.

They took top-cited papers from a variety of journals, and ranked them by title length (in number of characters), and number citations received (as of November 2014). Then they performed a Kendall's tau test to see whether these rankings are correlated. A negative correlation would mean that the articles with longer titles tend to be ranked low for citations.

The file `R/data/Letchford_2015_data.csv` contains the data needed to replicate their results.

- Write a program that performs the test described above using all the papers published in 2010. The program should do the following: 1) read the data; 2) extract all the papers published in 2010; 3) rank the articles by citations, and by title length; 4) compute the Kendall's tau expressing the correlation between the two rankings. For this dataset, the Authors get a tau of about -0.07 with a significant p-value.

First, let's read the data:
```{r}
l2015 <- read.table("../data/Letchford_2015_data.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE, quote = '"')
head(l2015)
```

Now extract those published in 2010
```{r}
papers_2010 <- subset(l2015, l2015$year == 2010)
papers_2010$titlerank <- rank(papers_2010$title_length)
papers_2010$citesrank <- rank(papers_2010$cites)
```

The Kendall's tau should be about -0.07

```{r}
cor(papers_2010$titlerank, papers_2010$citesrank, method = "kendall")
```

- Write a function that repeats the analysis for a particular journal-year combination. Try to run the function for the top scientific publications *Nature* and *Science*, and for the top medical journals *The Lancet* and *New Eng J Med*, for all years in the data (2007-2013). Do you always find a negative, significant correlation (i.e., negative tau with low p-value)?

```{r}
get_tau_jrn_year <- function(data, jrn, yr){
  jrn_yr <- subset(data, data$year == yr & data$journal == jrn)
  jrn_yr$titlerank <- rank(jrn_yr$title_length)
  jrn_yr$citesrank <- rank(jrn_yr$cites)
  return(cor(jrn_yr$titlerank, jrn_yr$citesrank))
}
```

Now we can try all the journals and years

```{r}
for (yr in 2007:2013){
  for (jr in c("Nature", "Science", "The Lancet", "New Eng J Med")){
   print(paste(jr, yr, get_tau_jrn_year(l2015, jr, yr))) 
  }
}
```

