## Self-incompatibility
> **Reviews:** Reading data, data frames, basic operations, string manipulation
>
> **Difficulty:** Easy

The file `R/data/Goldberg_2010.csv` contains the data from the paper by Goldberg et al. (Science 2010). In the csv file there is a list of 356 plant species and a Status describing whether the species is self-incompatible (0), self-compatible (1) or more complex situations (2-5).

- Write a program that counts how many species are in each category of Status. The output should be a dataframe, like
```
  Status count
1      0   116
2      1   196
3      2    17
4      3     1
5      4    25
6      5     1
```
First, we need to read the data:
```{r}
g2010 <- read.table("../data/Golberg_2010.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE)
```

The simplest solution is to use a for loop:
```{r}
# Determine the various Status and take only unique occurrences
status_values <- sort(unique(g2010$Status))

result <- data.frame()
# For each status, count the species and build a dataframe
for (st in status_values){
  num_sp <- sum(g2010$Status == st)
  result <- rbind(result, data.frame(Status = st, NumSpecies = num_sp))
}

print(result)
```

Alternatively, we can use the function `table`:

```{r}
tbl <- table(g2010$Status)
result <- data.frame(Status = names(tbl), NumSpecies = as.numeric(tbl))
print(result)
```

- Write another program that builds a table specifying how many species are in each Status for each genus (note that genus and species name are separated by an underscore in the first column).

We need a `Genus` column, obtained by splitting the string with the latin binomial. We can use `strsplit` in conjunction with a for loop:

```{r}
g2010$Genus <- rep("", dim(g2010)[1]) # initialize empty
for (i in 1:dim(g2010)[1]){
  g2010$Genus[i] <- strsplit(g2010$Species[i], "_")[[1]][1]  
}
head(g2010)
```

Now use `table` to get the result in one line of code:
```{r}
table(g2010$Genus, g2010$Status)
```

